\vspace{-5ex}\textbf{Multipoint Approximation Method for Large Scale Design Optimization Problems Under Uncertainty}

### 2017-04-12 2017/EUROGEN/eurogen.tex
EUROGEN: finish refs section

@@

Algorithm 1 (deterministic MAM).
\begin{enumerate}
\item Initialization: choose a starting point $\pmb x^0$ and initial trust region $[\pmb a^0, \pmb b^0]$ such that $\pmb x^0 \in [\pmb a^0, \pmb b^0]$.
\item At the $k$-th iteration the current approximation to the constrained minimum is $\pmb x^k$, the current trust region is $[\pmb a^k, \pmb b^k] \subset [\pmb a^0, \pmb b^0]$.
  \begin{enumerate}[label=(\alph*)]
    \item Design of Experiments (DoE): a set of points $\pmb x_k^i \in [\pmb a^k, \pmb b^k]$ is chosen to be used for approximation building. Responses are evaluated at the DoE points and approximations are built using the obtained values. Currently, the pool of approximation methods available in MAM consists of a metamodel assemblies15 and the moving least-squares metamodels16-19. Other metamodel types could be used as well.

    Denote the approximate objective function and constraints by $\widetilde{F}_0(\pmb x)$ and $\widetilde{F}_j(\pmb x)$, respectively.
    \item The original optimization problem (\ref{eq:problem}) is replaced by the following problem:
    \begin{equation}
      \label{eq:problem_approx}
      \begin{array}{c}
      \min\limits_{a_i^k \le x_i ^k\le b_i}\widetilde{F}_0(\pmb x) \\
      s.t.\; \widetilde{F}_j(\pmb x) \le 1,\; j=1,\dots ,M,
      \end{array}
    \end{equation}
    The approximate problem (\ref{eq:problem_approx}) is solved using Sequential Quadratic Programming (SQP) and the solution of this problem   determines the centre of the next trust region.
    \item The size of the next trust region is determined depending on the quality of approximations at the previous iteration, on the history of the points $\pmb x^k$, and on the size of the current trust region10.
    \item The termination criterion is checked (it is a part of the trust region strategy and depends on the position of the point $\pmb x^{k+1}$ in the current trust region, the size of the current trust region and the quality of approximations). If the termination criterion is satisfied, the algorithm proceeds to step 3. Otherwise, it returns to step 2.
  \end{enumerate}
  \item Optimization terminates. The obtained approximation to the solution of the problem (\ref{eq:problem}) is $\pmb x^{k+1}$.
\end{enumerate}

@@

As it has been already said, a risk measure is a mapping that transforms a random response $F(\pmb x+ \pmb u,\pmb y)$  into a deterministic function that can be optimized. Next we provide some examples of risk measures2,3.

\begin{itemize}
  \item $R(F)=\mu(F)$ where $\mu(F)$ is the mean of $F$. This choice corresponds to optimising average performance of the system. In typical engineering applications, however, this is not sufficient and more conservative risk measures need to be chosen.
  \item $R(F)=\sup(F)$. This is the most conservative case, in which one is concerned with the worst case performance of the system. The expression $\sup(F)$ stands for the least of all values that are greater than the random response $F$ with probability 1. If the support of the probability density function (PDF) of $F$ is not compact (i.e. $F$ can take arbitrary large values with non-zero probability) than $\sup(F)$ will be infinite.
  \item $R(F)=\mu(F)+k\sigma(F)$, where $\sigma(F)$ is the standard deviation of $F$ and $k>0$ is a constant. This risk measure is sometimes referred to as the safety margin. Optimisation using this risk measure is referred to as robust design optimisation22,23,24 and reflects the paradigms of a ‘$3\sigma$-design’, a ‘$6\sigma$-design’, etc.
  \item $R(F)=q_F(\alpha)$, where $q_F(\alpha)$ is the value of the quantile function, or simply the quantile, corresponding to a given probability $\alpha\in (0,1)$. This choice corresponds to the paradigm of reliability-based design optimization25,23,26. In this approach, one wants to keep the probability of the system failing (i.e. violating the constraint or underperforming, depending on the context) below a given threshold. The value $1-\alpha$ is the desired probability of failure. Although rather intuitive, this choice has known computational issues which are discussed by Rockafellar and Royset27.
\end{itemize}

@@

The dimension of these integrals is $n+n_e$. To compute them efficiently, methods of high-dimensional integration must be employed. Here, quasi-Monte-Carlo integration30 based on Niederreiter sequences31 is used.

@@

The example considered in this study is a classical engineering optimisation problem known as the scalable cantilevered beam34. The engineering object to be optimised is shown in Fig. \ref{fig:beam} taken from Ref. 34.

>>>>

The Moving Least Squares Method (MLSM) was proposed in Ref. \cite{LancasterSalkauskas1981} for smoothing and interpolation of scattered data and later used in the mesh-free form of the FEM\cite{Liszka1984}. As suggested in Ref.\cite{ChoiYounYang2001}, it can be used as a technique for metamodelling and used in MDO frameworks. The MLSM is a weighted least squares method where the weights depend on the Euclidian distance from a sample point to where the surrogate model is to be evaluated. The weight value for a certain sample point decays as the distance increases. Describing the weight decay with a Gaussian function tends to be the most useful option even though many others have been evaluated in Ref. \cite{ToropovSchrammSahaiJones2005}. As demonstrated in Ref. \cite{PolynkinToropov2010}, the cross-validated MLSM can be used both for design variable screening and for surrogate modelling. In order to create an efficient MDO framework for problems with disparate discipline attributes Ref. \cite{OllarToropovJones2014} extended the optimization approach of MAM to the use of local DOEs and MLS approximations built in different subspaces of the total design variable space corresponding to the individual disciplines. The subspaces are finally combined into the total design variable space in which the resulting MDO problem is solved.

@@

Algorithm 1 (deterministic MAM).
\begin{enumerate}
\item Initialization: choose a starting point $\pmb x^0$ and initial trust region $[\pmb a^0, \pmb b^0]$ such that $\pmb x^0 \in [\pmb a^0, \pmb b^0]$.
\item At the $k$-th iteration the current approximation to the constrained minimum is $\pmb x^k$, the current trust region is $[\pmb a^k, \pmb b^k] \subset [\pmb a^0, \pmb b^0]$.
  \begin{enumerate}[label=(\alph*)]
    \item Design of Experiments (DoE): a set of points $\pmb x_k^i \in [\pmb a^k, \pmb b^k]$ is chosen to be used for approximation building. Responses are evaluated at the DoE points and approximations are built using the obtained values. Currently, the pool of approximation methods available in MAM consists of a metamodel assemblies\cite{PolynkinToropov2012} and the moving least-squares metamodels\cite{LancasterSalkauskas1981,Liszka1984,ChoiYounYang2001,ToropovSchrammSahaiJones2005}. Other metamodel types could be used as well.

    Denote the approximate objective function and constraints by $\widetilde{F}_0(\pmb x)$ and $\widetilde{F}_j(\pmb x)$, respectively.
    \item The original optimization problem (\ref{eq:problem}) is replaced by the following problem:
    \begin{equation}
      \label{eq:problem_approx}
      \begin{array}{c}
      \min\limits_{a_i^k \le x_i ^k\le b_i}\widetilde{F}_0(\pmb x) \\
      s.t.\; \widetilde{F}_j(\pmb x) \le 1,\; j=1,\dots ,M,
      \end{array}
    \end{equation}
    The approximate problem (\ref{eq:problem_approx}) is solved using Sequential Quadratic Programming (SQP) and the solution of this problem   determines the centre of the next trust region.
    \item The size of the next trust region is determined depending on the quality of approximations at the previous iteration, on the history of the points $\pmb x^k$, and on the size of the current trust region\cite{KeulenToropovMarkine1996}.
    \item The termination criterion is checked (it is a part of the trust region strategy and depends on the position of the point $\pmb x^{k+1}$ in the current trust region, the size of the current trust region and the quality of approximations). If the termination criterion is satisfied, the algorithm proceeds to step 3. Otherwise, it returns to step 2.
  \end{enumerate}
  \item Optimization terminates. The obtained approximation to the solution of the problem (\ref{eq:problem}) is $\pmb x^{k+1}$.
\end{enumerate}

@@

As it has been already said, a risk measure is a mapping that transforms a random response $F(\pmb x+ \pmb u,\pmb y)$  into a deterministic function that can be optimized. Next we provide some examples of risk measures\cite{RockafellarUryasev2000,SchillingsSchulz2015}.

\begin{itemize}
  \item $R(F)=\mu(F)$ where $\mu(F)$ is the mean of $F$. This choice corresponds to optimising average performance of the system. In typical engineering applications, however, this is not sufficient and more conservative risk measures need to be chosen.
  \item $R(F)=\sup(F)$. This is the most conservative case, in which one is concerned with the worst case performance of the system. The expression $\sup(F)$ stands for the least of all values that are greater than the random response $F$ with probability 1. If the support of the probability density function (PDF) of $F$ is not compact (i.e. $F$ can take arbitrary large values with non-zero probability) than $\sup(F)$ will be infinite.
  \item $R(F)=\mu(F)+k\sigma(F)$, where $\sigma(F)$ is the standard deviation of $F$ and $k>0$ is a constant. This risk measure is sometimes referred to as the safety margin. Optimisation using this risk measure is referred to as robust design optimisation\cite{KochYangGu2004,Yao2011,ZhangZhuChenArendt2013} and reflects the paradigms of a ‘$3\sigma$-design’, a ‘$6\sigma$-design’, etc.
  \item $R(F)=q_F(\alpha)$, where $q_F(\alpha)$ is the value of the quantile function, or simply the quantile, corresponding to a given probability $\alpha\in (0,1)$. This choice corresponds to the paradigm of reliability-based design optimization\cite{AouesChateauneuf2010,Yao2011,YounChoi2004}. In this approach, one wants to keep the probability of the system failing (i.e. violating the constraint or underperforming, depending on the context) below a given threshold. The value $1-\alpha$ is the desired probability of failure. Although rather intuitive, this choice has known computational issues which are discussed by Rockafellar and Royset\cite{RockafellarRoyset2010}.
\end{itemize}

@@

The dimension of these integrals is $n+n_e$. To compute them efficiently, methods of high-dimensional integration must be employed. Here, quasi-Monte-Carlo integration\cite{Caflisch1998} based on Niederreiter sequences\cite{Niederreiter1992} is used.

@@

The example considered in this study is a classical engineering optimisation problem known as the scalable cantilevered beam\cite{Vanderpllaats2001}. The engineering object to be optimised is shown in Fig. \ref{fig:beam} taken from Ref. \cite{Vanderpllaats2001}.
